---
title: "dummy"
author: "K.Anoban"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

'---
title: "dummy"      
author: "K.Anoban"     
date: "`r Sys.Date()`"      
output: html_document        
---'

#### **The above chunk is a YAML syntax!!! Note the key:value pairs!!**  
**This section is designated for metadata!**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# This is a dummy analysys of COVID 19 dataset
```{r, echo = TRUE}
data <- read.csv("D:/Covid/covid-data.csv")
object.size(data)
```
```{r}
89981528/(1024^2)
```
Loaded data appears to be 85 MiBs in size!
```{r}
data |> colnames()
```
```{r, echo = TRUE}
data |> subset(continent == "Asia", select = c(new_cases, new_deaths)) |> summary()
```
```{r, echo = TRUE}
unique(data$continent)
```
```{r}
library(ggplot2)
oceania <- data |> 
    subset(continent == "Oceania", select = c(location, new_deaths, new_cases, date)) |> 
    transform(date = as.Date(strptime(date, "%Y-%m-%d"))) |> 
    subset(!is.na(location) & !is.na(new_deaths) & !is.na(new_cases), !is.na(date))
head(oceania, 5)
```

```{r}
object.size(oceania)
```

```{r}
150776/(1024^2)
```

```{r}
range(oceania$date)
```

```{r}
oceania |> ggplot(aes(x = date, col = location)) +
    geom_point(aes(y = new_deaths)) +
    ggtitle("Daily deaths caused by COVID 19 in Oceania from March 2020 to March 2022") +
    ylab("Deaths") +
    xlab("Date") + 
    theme_bw()
```      
```{r}
oceania |> ggplot(aes(x = date, col = location)) +
    geom_point(aes(y = new_cases)) +
    scale_y_log10() +
    ggtitle("Daily new COPVID 19 cases in Oceania from March 2020 to March 2022") +
    ylab("New cases") +
    xlab("Date") +
    theme_bw()
```     

### **There appears to be oscillating peaks in new cases in most countries in Oceania!**   
**The trend is not an overall decline as one would have expected but a rather slow rise with occassional spikes!**    
```{r, fig.align='center', fig.height=8, fig.width=10}
oceania |> ggplot(aes(x = location, y = new_deaths, fill = location)) +
    geom_boxplot() +
    scale_y_log10() +
    ylab("New deaths (log10)") +
    xlab("Country") +
    theme(axis.text.x = element_text(angle = 90)) 
```

One can include lists in R markdown docs! Here's an example!   

* Element 1
* Element 2
* Element 3
* Element 4

